COG-ED Manuscript

### 2021-10-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  # we will add the package versions before submission

@@

  dprime$falsealarmrate.z = NA
  dprime$hitrate.z = NA

@@

  dprime$d <- dprime$hitrate - dprime$falsealarmrate

@@

      h1a_data <- dprime[dprime$level != 1,]      # FIXME: Westbrook et al. exclude level 1, do you understand why?
      h1a_data$level <- as.factor(h1a_data$level)

@@

  # FIXME:  rmANOVA
      library(ez) # compute repeated measurement ANOVA
      h1a_data$subject <- factor(h1a_data$subject)
      # if there are reasonable concerns that we have NAs within our data set, we need to exclude this data beforehand

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  library(ez)           # compute repeated measures ANOVA
  # we will add the package versions before submission

@@

  dprime$hitrate.z = NA
  dprime$falsealarmrate.z = NA

@@

  dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z

@@

      h1a_data <- dprime[dprime$level != 1, ]
      h1a_data$level <- as.factor(h1a_data$level)

@@

  # FIXME:  rmANOVA
      h1a_data$subject <- factor(h1a_data$subject)
      # if there are reasonable concerns that we have NAs within our data set, we need to exclude this data beforehand
